How to select predictive models for decision-making or causal inference?

### 2023-12-17 how_to_select_causal_models.tex
iter

@@

\setlength{\marginparwidth}{0.5cm}
%\setlength\textwidth{177.8mm}

@@

For the regression step, we fit a Ridge regression on the transformed features
with 6 different choices of the regularization parameter $\lambda \in [10^{-3},
        10^{-2}, 10^{-1}, 1, 10^{1}, 10^{2}]$, coupled with a TLearner or a SftLearner.
We sample 10 different random basis for learning and
featurization yielding a family $\mathcal F$ of 120 candidate estimators.
%

>>>>

% TODO commands
\usepackage{snaptodo}
\setlength{\marginparwidth}{2.3cm}
\setlength{\marginparsep}{.1cm}
\snaptodoset{block rise=2em}
\snaptodoset{margin block/.style={font=\tiny}}

\newcommand{\gv}[1]{\snaptodo[margin block/.append style=green!50!black]{\sloppy\textbf{GV}: #1}}

% Uncomment below to erase all comments
%\renewcommand{\snaptodo}[2][1]{\relax}

@@

%\setlength{\marginparwidth}{0.5cm}
%\setlength\textwidth{177.8mm}

@@

For the regression step, we fit a Ridge regression on the transformed features
with 6 different choices of the regularization parameter $\lambda \in [10^{-3},
        10^{-2}, 10^{-1}, 1, 10^{1}, 10^{2}]$, coupled with a TLearner or
a SftLearner\gv{Si je lis bien, on n'utilise pas le SLearner. On pourrait
le retirer de la liste au dessus}.
We sample 10 different random basis for learning and
featurization yielding a family $\mathcal F$ of 120 candidate estimators.
%
